### 2015-06-10 LOI/inc2.tex
Fitting in 2 page again
add the variable parittioning thing that scott mentioned

\underline{\textbf{Objectives:}} Exascale scientific discovery will be
severely bottlenecked without sufficient new research into managing and
storing the large amounts of data that will be produced during the
simulation, and analyzed for months afterwards. In this project we will
demonstrate novel techniques to  facilitate efficient mapping of data from
the user space onto multiple storage tiers, and enable application-guided
data reductions/transformations to address capacity and bandwidth
bottlenecks. 
Our goal in this project is
to address the associated I/O and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into mission
critical scientific processes; which is associated with {\bf theme two} of the FOA. To that end, we will build on the
capabilities offered by ADIOS and DataSpaces at ORNL that provide I/O abstractions
and services, the Sirocco peer-to-peer file system at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions.    This project
brings together a  team with strong expertise in I/O middleware (ORNL, Rutgers), file system (SNL, UCSC) and storage (UCSC), and connects and
coordinates these key storage components in a seamless fashion.

>>>>

\underline{\textbf{Objectives:}} Exascale scientific discovery will be
severely bottlenecked without sufficient new research into managing and
storing the large amounts of data that will be produced during the
simulation, and analyzed for months afterwards. In this project we will
demonstrate novel techniques to  facilitate efficient mapping of data
objects, even partitioning individual variables, from
the user space onto multiple storage tiers, and enable application-guided
data reductions/transformations to address capacity and bandwidth
bottlenecks. 
Our goal in this project is
to address the associated I/O and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into mission
critical scientific processes; which is associated with {\bf theme two} of the FOA. To that end, we will build on the
capabilities offered by ADIOS and DataSpaces at ORNL that provide I/O abstractions
and services, the Sirocco peer-to-peer file system at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions.    This project
brings together a  team with strong expertise in I/O middleware (ORNL, Rutgers), file system (SNL, UCSC) and storage (UCSC), and connects and
coordinates these key storage components in a seamless fashion.
